A 38 Million Year Old Mini-Neptune in the Kepler Field

### 2021-11-24 paper/ms.tex
[WIP] review #1 most comments addressed

%\documentclass[12pt,modern,twocolumn,tighten]{aastex63}
\documentclass[12pt,modern,twocolumn,tighten,linenumbers]{aastex63}
%\documentclass[12pt,twocolumn,tighten,linenumbers]{aastex63}
%\documentclass[12pt,twocolumn,tighten,trackchanges]{aastex63}
\usepackage{amsmath,amstext,amssymb}
\usepackage[T1]{fontenc}
\usepackage{apjfonts}
\usepackage[figure,figure*]{hypcap}
\usepackage{graphics,graphicx}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage[caption=false]{subfig} % for subfloat
\usepackage{enumitem} % for specific spacing of enumerate
\usepackage{epigraph}

@@

% 208 words (250 max)
\begin{abstract}
  Kepler\,1627A is a G8V star previously known to host a
  $3.8\,R_\oplus$ mini-Neptune on a 7.2\,day orbit.  The star was
  observed by the Kepler space telescope because it is nearby
  ($d=329\,{\rm pc}$) and it resembles the Sun.  Here we show using
  Gaia kinematics, TESS stellar rotation periods, and spectroscopic
  lithium abundances that Kepler\,1627 is a member of the \clusterage\
  old $\delta$~Lyr cluster.  To our knowledge, this makes
  Kepler\,1627Ab the youngest planet with a precise age yet found by
  the main Kepler mission.  The Kepler photometry shows two
  peculiarities: the average transit profile is asymmetric, and the
  individual transit times might be correlated with the local light curve
  slope.  We discuss possible explanations for each anomaly.  More
  importantly, the $\delta$~Lyr cluster
  is one of $\sim$10$^3$ coeval groups whose properties have been clarified
  by Gaia.  Many other exoplanet hosts are candidate members
  of these clusters; these memberships can be verified with the
  trifecta of Gaia, TESS, and ground-based spectroscopy.
\end{abstract}

@@

For instance, the ``mini-Neptunes'', thought to be made of metal
cores, silicate mantles \citep{kite_atmosphere_2020}, and extended
hydrogen-dominated atmospheres, are expected to shrink
in size by factors of several over their first $10^8$ years.
Specifically, in the models of \citet{owen_atmospheres_2016} and
\citet{owen_constraining_2020}, the $\approx$$5\,M_\oplus$ planets start
with sizes of 4\,--\,12\,$R_\oplus$ shortly after the time of disk
dispersal ($\lesssim$$10^7$\,years), and shrink to sizes of
2\,--\,4\,$R_\oplus$ by 10$^8$ years.  While the majority of this change
is expected to occur within the first few million years after the disk
disperses \citep{ikoma_situ_2012}, stellar
irradiation and internal heat can also power gradual outflows
which, if strong enough, can deplete or entirely strip the atmosphere \citep{Owen_Wu_2013,ginzburg_corepowered_2018}.
Discovering young planets, measuring their masses, and detecting their
atmospheric outflows are key steps toward testing this paradigm, which
is often invoked to explain the observed radius distribution of mature
exoplanets \citep{Fulton_et_al_2017,van_eylen_asteroseismic_2018}.

The K2 and TESS missions have now enabled the detection of about ten
close-in planets younger than 100 million years, all smaller than
Jupiter
\citep{Mann_K2_33b_2016,David_et_al_2017,david_four_2019,newton_tess_2019,bouma_cluster_2020,plavchan_planet_2020,rizzuto_tess_2020,martioli_aumicbc_2021}.
The Kepler mission however has not yielded any planets with precise
ages below one gigayear \citep{Meibom_et_al_2013}.  The reason is that
during the main Kepler mission (2009--2013), only four open clusters
were known in the Kepler field,
%: NGC\,6866, NGC\,6811, NGC\,6819, and NGC\,6791,
with ages spanning 0.7\,Gyr to 9\,Gyr \citep{meibom_kepler_2011}.
Though isochronal, gyrochronal, and lithium-based analyses suggest
that younger Kepler planets do exist
\citep{berger_identifying_2018,david_sizes_2021}, accurate and precise
age measurements typically require an ensemble of stars.  Fortunately,
recent analyses of the Gaia data have greatly expanded our knowledge
of cluster memberships \citep[{\it
e.g.},][]{CantatGaudin2018a,Zari2018,KounkelCovey2019,Meingast2021,Kerr2021}.
As part of our Cluster Difference Imaging Photometric Survey (CDIPS,
\citealt{bouma_cdipsI_2019}), we concatenated the available analyses
from the literature, which yielded a list of candidate young and
age-dated stars (see Appendix~\ref{app:targetlist}).

@@

\citet{KounkelCovey2019} applied an unsupervised clustering algorithm
to Gaia DR2 on-sky positions, proper motions, and parallaxes for stars
within the nearest kiloparsec.  For the \cn\ (Theia 73), they reported
\noriginal\ candidate members.  We matched these stars against the
latest Gaia EDR3 observations using the \texttt{dr2\_neighbourhood}
table from the ESA archive,
taking the stars closest in proper motion and epoch-corrected angular
distance as the presumed match \citep{gaia_collaboration_2021_edr3}.
In Figure~\ref{fig:XYZvtang}, have shown galactic positions only for
the stars with parallax signal-to-noise exceeding 20.  The reported
cluster members (gray and black points) extend over a much larger
volume than the cluster previously identified by
\citet{stephenson_possible_1959} and later corroborated by
\citet{eggen_photometric_1968}.  While the non-uniform ``clumps'' of
stars might comprise a {\it bona fide} cluster of identically-aged
stars, they could also be heavily contaminated by field stars.  We
therefore considered stars only in the immediate kinematic and spatial
vicinity of \sn\ as candidate cluster members.  We performed the
selection cuts manually, by drawing lassos with the interactive
\texttt{glue} visualization tool \citep{beaumont_2014_13866} in the
four projections shown in Figure~\ref{fig:XYZvtang}.  The overlap
between the Kepler field and the resulting candidate cluster members
is shown in Figure~\ref{fig:skychart}.  While this method will include
some field interlopers in the ``cluster star'' sample, and vice-versa,
it should suffice for our aim of verifying the existence of the
cluster in the vicinity of \sn.

@@

We measured the isochrone age using an empirical approach.  The left
panel of Figure~\ref{fig:age} shows the color-absolute magnitude
diagram (CAMD) of candidate \cn\ members, IC\,2602, the Pleiades, and
the field.  The stars from the Pleiades and IC\,2602 were adopted from
\citet{CantatGaudin2018a}, and the field stars are from the Gaia EDR3
Catalog of Nearby Stars \citep{gaia_gcns_2021}.  We cleaned these
following the data filtering criteria from \citet[][Appendix
B]{GaiaCollaboration2018}, except that we weakened the parallax
precision requirement to $\varpi/\sigma_\varpi>5$.  These filters were
designed to include genuine binaries while omitting instrumental
artifacts.  We then corrected for extinction by querying the
3-dimensional maps of \citet{capitanio_threedimensional_2017} and
\citet{lallement_threedimensional_2018}\footnote{\url{https://stilism.obspm.fr/},
2021/09/25}, and applied the extinction coefficients $k_X\equiv
A_X/A_0$ computed by \citet{GaiaCollaboration2018} assuming that $A_0
= 3.1 E(B-V)$.  For IC\,2602, the Pleiades, and the \cn, this
procedure yielded a respective mean and standard deviation for the
reddening of $E(B-V)=\{0.020\pm0.003, 0.045\pm0.008, 0.032\pm0.006\}$.
These values agree reasonably well with previously reported values
from the literature \citep[{\it
e.g.},][]{GaiaCollaboration2018,KounkelCovey2019,bossini_age_2019}.

@@

Figure~\ref{fig:age} shows that the \cn\ and IC\,2602 overlap, and
therefore are approximately the same age.  In our exploration, we also
compared against $\mu$-Tau ($62\pm7$\,Myr; \citealt{gagne_mutau_2020})
and the Upper-Centaurus-Lupus (UCL) component of the Sco OB2
association ($\approx$$16$\,Myr; \citealt{pecaut_star_2016}).  The
pre-main-sequence M dwarfs of the \cn\ were intermediate between the
latter two clusters.  To turn this heuristic interpolation into an age
measurement, we used the empirical method developed by
\citet{gagne_mutau_2020}.  In brief, we fitted the pre-main-sequence
loci of a set of reference clusters, and the locus of the target \cn\
was then modeled as a piecewise linear combination of these reference
clusters.  For our reference clusters, we adopted members of UCL,
IC\,2602, and the Pleiades from \citet{Damiani2019} and
\cite{CantatGaudin2018a} respectively.  We removed binaries by
requiring $\texttt{RUWE}<1.3$, $\texttt{radial\_velocity\_error}$
below the 80$^{\rm th}$ percentile of each cluster's distribution, and
excluded stars that were obvious photometric binaries in the CAMD.  We
then passed a moving box average and standard deviation across the
CAMD in 0.10\,mag bins, fitted a univariate spline to the binned
values, and assembled a piecewise grid of hybrid isochrones spanning
the ages between UCL to the Pleiades using Equations~6 and~7 from
\citet{gagne_mutau_2020}.

@@

Of the \noriginal\ candidate \cn\ members reported by
\citet{KounkelCovey2019}, \nwithtess\ stars were amenable to rotation
period measurements ($G<17$ and $\bpmrpo>0.5$) using the TESS full
frame image data. 
We extracted light curves from
the TESS images using the nearest pixel to each star, and regressed
them against systematics with the causal pixel model implemented in
the \texttt{unpopular} package \citep{hattorio_2021_cpm}.  We then
measured candidate rotation periods using a Lomb-Scargle periodogram
\citep{lomb_1976,scargle_studies_1982,astropy_2018}.  To enable cuts
on crowding, we queried the Gaia source catalog for stars within a
$21\farcs0$ radius of the target star (a radius of 1 TESS pixel).
Within this radius, we recorded the number of stars with greater
brightness than the target star, and with brightness within 1.25 TESS magnitudes of the target star.

We then cleaned the candidate TESS rotation period measurements
through a combination of automated and manual steps.  As a matter of
scope, we restricted our attention to the \nkinwithtess\ stars
discussed in Section~\ref{sec:kinematicselection} in the spatial and
kinematic proximity of Kepler\,1627.  
Kepler rotation periods were derived by
\citet{mcquillan_rotation_2014} for 28 of these stars; for these cases, we
simply adopted the Kepler rotation period.
For the remaining stars with only TESS data, we
focused only on the stars for which no companions were known with a brightness
exceeding one-tenth of the target star in a $21\farcs0$ radius.  There
were \nkinwithtessandcrowding\ stars that met these crowding requirements, and
that had TESS data available.  For plotting purposes we then imposed a
selection based on the strength of the signal itself: we required the
Lomb Scargle power to exceed 0.2, and the period to be below 15\,days.

The lower panel of Figure~\ref{fig:age} shows the resulting
\nkindefaultcleaning\ stars.  
The majority of these stars fall below
the ``slow sequence'' of the Pleiades, consistent with a gyrochronal
age for the \cn\ below 100\,Myr.  In fact, the rotation-color
distributions of other 30\,Myr to 50\,Myr clusters ({\it e.g.},
IC\,2602 and IC\,2391) are indistinguishable
\citep{douglas_stephanie_t_2021_5131306}.  Approximately 10 of the
\cn\ stars appear as outliers above the ``slow sequence''.  Assuming
that they are all false positives ({\it i.e.}, field interlopers), our
rotation period detection fraction would be
$\nrotgood/\nkinwithtessandcrowding \approx \nfracprot\%$.   The other
stars are likely to be field contaminants.  A final possible
confounding factor -- binarity -- is known to affect the ``fast
sequence'' of stars beneath the slow sequence
\citep{meibom_effect_2007,gillen_ngts_2020,bouma_2021_ngc2516}.  We do
not expect it to change the central conclusion regarding the cluster's
age.

@@

% \footnote{\url{http://www.pas.rochester.edu/~emamajek/EEM_dwarf_UBVIJHK_colors_Teff.txt}, version \texttt{2021/03/02}.}
Figure~\ref{fig:kep1627binary} summarizes the results of the
high-resolution imaging.  The Gaia EDR3 parallax for the primary
implies a projected separation of $53 \pm 4$\,AU, assuming the
companion is bound.  Although the companion is unresolved in the Gaia
source catalog (there are no comoving, codistant candidate companions
brighter than $G < 20.5$ mag within $\rho < 120\arcsec$), its
existence was also suggested by the primary star's large renormalized
unit weight error (RUWE), relative to other members of the \cn.  Based
on the apparent separation, the binary orbital period is of order
hundreds of years.  The large RUWE is therefore more likely to be
caused by a PSF-mismatch skewing the Gaia centroiding during
successive scans, rather than true astrometric motion.  Regardless,
given the low geometric probability that a companion imaged at $\rho
\approx 0\farcs16$ is a chance line-of-sight companion, we proceed
under the assumption that the companion is bound, and that
Kepler\,1627 is a binary.  Given the distance and age, the models of
\citet{baraffe_new_2015} imply a companion mass of $M_{\rm B} \approx
0.33 M_{\odot}$ and companion temperature of $T_{\rm eff,B} \approx
3450$ K.  The corresponding spectral type is roughly M2.5V
\citep{pecaut_mamajek_2013}.  These models combined with the NIRC2
contrast limits imply physical limits on tertiary companions of
$M_{\rm ter} < 50 M_{\rm Jup}$ at $\rho = 50$\,AU, $M_{\rm ter} < 20
M_{\rm Jup}$ at $\rho = 100$\,AU, and $M_{\rm ter} < 10 M_{\rm Jup}$
at $\rho = 330$\,AU.

@@

		\vspace{-0.2cm}	
		\subfloat{
			\includegraphics[width=0.5\textwidth]{f5b.pdf}
			\includegraphics[width=0.5\textwidth]{f5c.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
  \caption{ {\bf The light curve of Kepler\,1627.}
    {\it Top}: 
    The Kepler data span 1{,}437 days (3.9 years), sampled at 30
    minute cadence;  a 100 day segment is shown.  The top panel shows
    the \texttt{PDCSAP} median-subtracted flux in units of
    parts-per-thousand ($\times 10^{-3}$).  The dominant signal is
    induced by starspots.  The stellar variability model (orange line)
    is subtracted below, revealing the transits of \pn.  The online
    Figure Set spans the entire 3.9 years of observations.
    {\it Bottom}:
    Phase-folded transit of Kepler 1627Ab with stellar variability
    removed.  Windows over 20 hours ({\it left}) and the entire orbit
    ({\it right}) are shown, and the residual after subtracting the
    transit is in the bottom-most row.  The 2-$\sigma$ model uncertainties
    and the best-fit model are the light purple band and the dark
    purple line.  Gray points are individual flux measurements; black
    points bin these to 20 minute intervals, and have a representative
    1-$\sigma$ error bar in the lower right of each panel.  The asymmetric
    residual during transit is larger than the out-of-transit scatter.
    \label{fig:lc}
  }
\end{figure*}

The Kepler space telescope observed \sn\ at a 30-minute cadence from
2009 May 2 until 2013 April 8.  Data gaps during quarters 4, 9, and 13
led to an average duty cycle over the 3.9~year interval of 67\%.  \sn\
was also observed at 1-minute cadence from 2012 Oct 5 until 2013 Jan
11.  The top panel of Figure~\ref{fig:lc} shows a portion of the
30-minute cadence \texttt{PDCSAP} light curve.  Nonastrophysical
variability has been removed using the methods discussed by
\citet{smith_kepler_PDC_2017}; the default optimal aperture was
assumed \citep{smith_finding_2016}.  Cadences with non-zero quality
flags (9\% of the data) have been omitted.  The resulting photometry
is dominated by a quasi-periodic starspot signal with a peak-to-peak
amplitude that varies between 2\% and 8\%.  Previous analyses have
identified and characterized the smaller transit signal
\citep{2012ApJS..199...24T,thompson_planetary_2018}, validated its
planetary nature \citep{morton_false_2016}, and even searched the
system for transit timing variations \citep{holczer_transit_2016}.
Nonetheless, since the cluster membership provides us with more
precise stellar parameters than those previously available, we opted
to reanalyze the light curve.

@@

The most crucial parameters of a given star for our purposes are the
Gaia DR2 $\texttt{source\_id}$, the cluster or group name
($\texttt{cluster}$), and the $\texttt{age}$.  Given the hierarchical
nature of many stellar associations, we do not attempt to resolve the
cluster names to a single unique string.  The Orion complex for
instance can be divided into almost one hundred kinematic subgroups
\citep{kounkel_apogee2_2018}.  Similar complexity applies to the
problem of determining homogeneous ages, which we do not attempt to
resolve.  Instead, we simply merged the cluster names and ages
reported by various authors into a comma-separated string.

>>>>

%\documentclass[12pt,modern,twocolumn,tighten]{aastex63}
%\documentclass[12pt,modern,twocolumn,tighten,linenumbers]{aastex63}
\documentclass[12pt,modern,twocolumn,tighten,linenumbers,trackchanges]{aastex63}
%\documentclass[12pt,twocolumn,tighten,linenumbers]{aastex63}
%\documentclass[12pt,twocolumn,tighten,trackchanges]{aastex63}
\usepackage{amsmath,amstext,amssymb}
\usepackage[T1]{fontenc}
\usepackage{apjfonts}
\usepackage[figure,figure*]{hypcap}
\usepackage{graphics,graphicx}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage[caption=false]{subfig} % for subfloat
\usepackage{enumitem} % for specific spacing of enumerate
\usepackage{epigraph}

@@

% 208 words (250 max)
\begin{abstract}
  Kepler\,1627A is a G8V star previously known to host a
  $3.8\,R_\oplus$ mini-Neptune on a 7.2\,day orbit.  The star was
  observed by the Kepler space telescope because it is nearby
  ($d=329\,{\rm pc}$) and it resembles the Sun.  Here we show using
  Gaia kinematics, TESS stellar rotation periods, and spectroscopic
  lithium abundances that Kepler\,1627 is a member of the \clusterage\
  old $\delta$~Lyr cluster.  To our knowledge, this makes
  Kepler\,1627Ab the youngest planet with a precise age yet found by
  the main Kepler mission.  The Kepler photometry shows two
  peculiarities: the average transit profile is asymmetric, and the
  individual transit times might be correlated with the local light curve
  slope.  We discuss possible explanations for each anomaly.  More
  importantly, the $\delta$~Lyr cluster
  is one of $\sim$10$^3$ coeval groups whose properties have been clarified
  by Gaia.  Many other exoplanet hosts are candidate members
  of these clusters; their ages can be verified \replaced{through}{with} the
  trifecta of Gaia, TESS, and ground-based spectroscopy.
\end{abstract}

@@

For instance, the ``mini-Neptunes'', thought to be made of metal
cores, silicate mantles \citep{kite_atmosphere_2020}, and extended
hydrogen-dominated atmospheres, are expected to shrink
in size by factors of several over their first $10^8$ years.
Specifically, in the models of \citet{owen_atmospheres_2016} and
\citet{owen_constraining_2020}, the $\approx$$5\,M_\oplus$ planets start
with sizes of 4\,--\,12\,$R_\oplus$ shortly after the time of disk
dispersal ($\lesssim$$10^7$\,years), and shrink to sizes of
2\,--\,4\,$R_\oplus$ by 10$^8$ years.  While the majority of this change
is expected to occur within the first few million years after the disk
disperses \citep{ikoma_situ_2012}, stellar
irradiation and internal heat can also power gradual outflows
which, if strong enough, can deplete or entirely strip the atmosphere \citep{lopez_how_2012,Owen_Wu_2013,ginzburg_corepowered_2018}.
Discovering young planets, measuring their masses, and detecting their
atmospheric outflows are key steps toward testing this paradigm, which
is often invoked to explain the observed radius distribution of mature
exoplanets \citep{Fulton_et_al_2017,van_eylen_asteroseismic_2018}.

The K2 and TESS missions have now enabled the detection of about ten
close-in planets younger than 100 million years, all smaller than
Jupiter
\citep{Mann_K2_33b_2016,David_et_al_2017,david_four_2019,newton_tess_2019,bouma_cluster_2020,plavchan_planet_2020,rizzuto_tess_2020,martioli_aumicbc_2021}.
The Kepler mission however has not yielded any planets with precise
ages below one gigayear \citep{Meibom_et_al_2013}.  The reason is that
during the main Kepler mission (2009--2013), only four open clusters
were known in the Kepler field,
%: NGC\,6866, NGC\,6811, NGC\,6819, and NGC\,6791,
with ages spanning 0.7\,Gyr to 9\,Gyr \citep{meibom_kepler_2011}.
Though isochronal, gyrochronal, and lithium-based analyses suggest
that younger Kepler planets do exist
\citep{walkowicz_rotation_2013,berger_identifying_2018,david_sizes_2021}, accurate and precise
age measurements typically require an ensemble of stars.  Fortunately,
recent analyses of the Gaia data have greatly expanded our knowledge
of cluster memberships \citep[{\it
e.g.},][]{CantatGaudin2018a,Zari2018,KounkelCovey2019,Meingast2021,Kerr2021}.
As part of our Cluster Difference Imaging Photometric Survey (CDIPS,
\citealt{bouma_cdipsI_2019}), we concatenated the available analyses
from the literature, which yielded a list of candidate young and
age-dated stars (see Appendix~\ref{app:targetlist}).

@@

\citet{KounkelCovey2019} applied an unsupervised clustering algorithm
to Gaia DR2 on-sky positions, proper motions, and parallaxes for stars
within the nearest kiloparsec.  For the \cn\ (Theia 73), they reported
\noriginal\ candidate members.  We matched these stars against the
latest Gaia EDR3 observations using the \texttt{dr2\_neighbourhood}
table from the ESA archive,
taking the stars closest in proper motion and epoch-corrected angular
distance as the presumed match \citep{gaia_collaboration_2021_edr3}.
In Figure~\ref{fig:XYZvtang}, have shown galactic positions only for
the stars with parallax signal-to-noise exceeding 20.  The reported
cluster members (gray and black points) extend over a much larger
volume than the cluster previously identified by
\citet{stephenson_possible_1959} and later corroborated by
\citet{eggen_photometric_1968}.  While the non-uniform ``clumps'' of
stars might comprise a {\it bona fide} cluster of identically-aged
stars, they could also be heavily contaminated by field stars.  We
therefore considered stars only in the immediate kinematic and spatial
vicinity of \sn\ as candidate cluster members.  We performed the
selection cuts manually, by drawing lassos with the interactive
\texttt{glue} visualization tool \citep{beaumont_2014_13866} in the
four projections shown in Figure~\ref{fig:XYZvtang}.  The overlap
between the Kepler field and the resulting candidate cluster members
is shown in Figure~\ref{fig:skychart}.  While this method will include
some field interlopers in the ``cluster star'' sample, and vice-versa,
it should suffice for our aim of verifying the existence of the
cluster in the vicinity of \sn.
%\added{The application of a more careful membership selection procedure to the $\delta$\ Lyr\ cluster (as part of a larger complex spanning Cepheus and Hercules) is a topic under current investigation by by R.~Kerr and collaborators.}

@@

We measured the isochrone age using an empirical approach.  The left
panel of Figure~\ref{fig:age} shows the color-absolute magnitude
diagram (CAMD) of candidate \cn\ members, IC\,2602, the Pleiades, and
the field.  The stars from the Pleiades and IC\,2602 were adopted from
\citet{CantatGaudin2018a}, and the field stars are from the Gaia EDR3
Catalog of Nearby Stars \citep{gaia_gcns_2021}.  We cleaned these
following the data filtering criteria from \citet[][Appendix
B]{GaiaCollaboration2018}, except that we weakened the parallax
precision requirement to $\varpi/\sigma_\varpi>5$.  \added{This also involved cuts
on the photometric signal to noise ratio, the number of visibility
periods used, the astrometric $\chi^2$ of the single-source solution, and the
$G_{\rm BP}-G_{\rm RP}$ color excess factor.} These filters were
designed to include genuine binaries while omitting instrumental
artifacts.  We then corrected for extinction by querying the
3-dimensional maps of \citet{capitanio_threedimensional_2017} and
\citet{lallement_threedimensional_2018}\footnote{\url{https://stilism.obspm.fr/},
2021/09/25}, and applied the extinction coefficients $k_X\equiv
A_X/A_0$ computed by \citet{GaiaCollaboration2018} assuming that $A_0
= 3.1 E(B-V)$.  For IC\,2602, the Pleiades, and the \cn, this
procedure yielded a respective mean and standard deviation for the
reddening of $E(B-V)=\{0.020\pm0.003, 0.045\pm0.008, 0.032\pm0.006\}$.
These values \replaced{agree reasonably well with}{are within a
factor of two of} previously reported values
\replaced{from}{in} the literature \citep[{\it
e.g.},][]{GaiaCollaboration2018,KounkelCovey2019,bossini_age_2019}\added{,
and are all small enough that the choice of whether to use them {\it vs.} other
extinction estimates does not affect our primary conclusions}.

@@

Figure~\ref{fig:age} shows that the \cn\ and IC\,2602 overlap, and
therefore are approximately the same age.  In our exploration, we also
compared against $\mu$-Tau ($62\pm7$\,Myr; \citealt{gagne_mutau_2020})
and the Upper-Centaurus-Lupus (UCL) component of the Sco OB2
association ($\approx$$16$\,Myr; \citealt{pecaut_star_2016}).  The
pre-main-sequence M dwarfs of the \cn\ were intermediate between the
latter two clusters.  To turn this heuristic interpolation into an age
measurement, we used the empirical method developed by
\citet{gagne_mutau_2020}.  In brief, we fitted the pre-main-sequence
loci of a set of reference clusters, and the locus of the target \cn\
was then modeled as a piecewise linear combination of these reference
clusters.  For our reference clusters, we adopted members of UCL,
IC\,2602, and the Pleiades from \citet{Damiani2019} and
\cite{CantatGaudin2018a} respectively.  We removed binaries by
requiring $\texttt{RUWE}<1.3$, $\texttt{radial\_velocity\_error}$
below the 80$^{\rm th}$ percentile of each cluster's distribution, and
excluded stars that were obvious photometric binaries in the CAMD.\footnote{
  For a description of the renormalized unit weight error (RUWE), see the GAIA DPAC technical note
  \url{http://www.rssd.esa.int/doc_fetch.php?id=3757412}.}  We then passed a
moving box average and standard deviation across the CAMD in 0.10\,mag bins,
fitted a univariate spline to the binned values, and assembled a
piecewise grid
of \deleted{hybrid }isochrones spanning the ages between UCL \replaced{to}{and} the Pleiades using
Equation\replaced{s~6 and~7}{6} from
\citet{gagne_mutau_2020}.  
\added{To derive a probability distribution function for the age of \cn, we
then assumed a Gaussian likelihood that treated the interpolated isochrones as
the ``model'' and the $\delta$\ Lyr\ cluster's isochrone as the ``data''
(Equation~7 from \citealt{gagne_mutau_2020}).  The cluster's age and its
statistical uncertainty are then quoted as the the mean and standard deviation
of this age posterior.}

@@

Of the \noriginal\ candidate \cn\ members reported by
\citet{KounkelCovey2019}, \nwithtess\ stars were amenable to rotation
period measurements ($G<17$ and $\bpmrpo>0.5$) using the TESS full
frame image data. 
\added{As a matter of
scope, we restricted our attention to the \nkinwithtess\ stars
discussed in Section~\ref{sec:kinematicselection} in the spatial and
kinematic proximity of Kepler\,1627. }
We extracted light curves from
the TESS images using the nearest pixel to each star, and regressed
them against systematics with the causal pixel model implemented in
the \texttt{unpopular} package \citep{hattorio_2021_cpm}.  We then
measured candidate rotation periods using a Lomb-Scargle periodogram
\citep{lomb_1976,scargle_studies_1982,astropy_2018}.  To enable cuts
on crowding, we queried the Gaia source catalog for stars within a
$21\farcs0$ radius of the target star (a radius of 1 TESS pixel).
Within this radius, we recorded the number of stars with greater
brightness than the target star, and with brightness within 1.25 TESS magnitudes of the target star.

We then cleaned the candidate TESS rotation period measurements
through a combination of automated and manual steps.  \deleted{As a matter of
scope, we restricted our attention to the \nkinwithtess\ stars
discussed in Section~\ref{sec:kinematicselection} in the spatial and
kinematic proximity of Kepler\,1627.}  
Kepler rotation periods were derived by
\citet{mcquillan_rotation_2014} for 28 of \replaced{these }{our \nkinwithtess\ }stars; for these cases, we
simply adopted the Kepler rotation period.
For the remaining stars with only TESS data, we
focused only on the stars for which no companions were known with a brightness
exceeding one-tenth of the target star in a $21\farcs0$ radius.  There
were \nkinwithtessandcrowding\ stars that met these crowding requirements, and
that had TESS data available.  For plotting purposes we then imposed a
selection based on the strength of the signal itself: we required the
Lomb Scargle power to exceed 0.2, and the period to be below 15\,days.

The lower panel of Figure~\ref{fig:age} shows the resulting
\nkindefaultcleaning\ stars.  
The majority of these stars fall below
the ``slow sequence'' of the Pleiades, consistent with a gyrochronal
age for the \cn\ below 100\,Myr.  In fact, the rotation-color
distributions of other 30\,Myr to 50\,Myr clusters ({\it e.g.},
IC\,2602 and IC\,2391) are indistinguishable\added{ from each other}
\citep{douglas_stephanie_t_2021_5131306}.  Approximately 10 of the
\cn\ stars appear as outliers above the ``slow sequence''.  Assuming
that they are all false positives ({\it i.e.}, field interlopers), our
rotation period detection fraction would be
$\nrotgood/\nkinwithtessandcrowding \approx \nfracprot\%$.   \replaced{The other
stars are likely to be field contaminants.}{Although some of these outlier stars might be
unresolved F+K binaries that are in the cluster
\citep{stauffer_rotation_2016}, assuming that they are field contaminants
provides a more secure lower bound of the rotation period detection fraction.}  A final possible
confounding factor -- binarity -- is known to affect the ``fast
sequence'' of stars beneath the slow sequence
\citep{meibom_effect_2007,gillen_ngts_2020,bouma_2021_ngc2516}.  We do
not expect it to change the central conclusion regarding the cluster's
age.

@@

% \footnote{\url{http://www.pas.rochester.edu/~emamajek/EEM_dwarf_UBVIJHK_colors_Teff.txt}, version \texttt{2021/03/02}.}
Figure~\ref{fig:kep1627binary} summarizes the results of the
high-resolution imaging.  The Gaia EDR3 parallax for the primary
implies a projected separation of $53 \pm 4$\,AU, assuming the
companion is bound.  Although the companion is unresolved in the Gaia
source catalog (there are no comoving, codistant candidate companions
brighter than $G < 20.5$ mag within $\rho < 120\arcsec$), its
existence was also suggested by the primary star's large \replaced{renormalized
unit weight error (RUWE),}{RUWE} relative to other members of the \cn\
\added{(RUWE$\approx$2.9; roughly the $98^{\rm th}$ percentile of the cluster's
distribution)}.  Based
on the apparent separation, the binary orbital period is of order
hundreds of years.  The large RUWE is therefore more likely to be
caused by a PSF-mismatch skewing the Gaia centroiding during
successive scans, rather than true astrometric motion.  Regardless,
given the low geometric probability that a companion imaged at $\rho
\approx 0\farcs16$ is a chance line-of-sight companion, we proceed
under the assumption that the companion is bound, and that
Kepler\,1627 is a binary.  Given the distance and age, the models of
\citet{baraffe_new_2015} imply a companion mass of $M_{\rm B} \approx
0.33 M_{\odot}$ and companion temperature of $T_{\rm eff,B} \approx
3450$ K.  The corresponding spectral type is roughly M2.5V
\citep{pecaut_mamajek_2013}.  These models combined with the NIRC2
contrast limits imply physical limits on tertiary companions of
$M_{\rm ter} < 50 M_{\rm Jup}$ at $\rho = 50$\,AU, $M_{\rm ter} < 20
M_{\rm Jup}$ at $\rho = 100$\,AU, and $M_{\rm ter} < 10 M_{\rm Jup}$
at $\rho = 330$\,AU.

@@

		\vspace{-0.2cm}	
		\subfloat{
			\includegraphics[width=0.5\textwidth]{f5b.pdf}
			\includegraphics[width=0.5\textwidth]{f5c.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
  \caption{ {\bf The light curve of Kepler\,1627.}
    {\it Top}: 
    The Kepler data span 1{,}437 days (3.9 years), sampled at 30
    minute cadence;  a 100 day segment is shown.  The top panel shows
    the \texttt{PDCSAP} median-subtracted flux in units of
    parts-per-thousand ($\times 10^{-3}$).  The dominant signal is
    induced by starspots.  The stellar variability model (orange line)
    is subtracted below, revealing the transits of \pn.  The online
    Figure Set spans the entire 3.9 years of observations.
    {\it Bottom}:
    Phase-folded transit of Kepler 1627Ab with stellar variability
    removed.  Windows over 20 hours ({\it left}) and the entire orbit
    ({\it right}) are shown, and the residual after subtracting the
    transit is in the bottom-most row.  The 2-$\sigma$ model uncertainties
    and the best-fit model are the light purple band and the dark
    purple line.  Gray points are individual flux measurements; black
    points bin these to 15 minute intervals, and have a representative
    1-$\sigma$ error bar in the lower right of each panel.  The asymmetric
    residual during transit is larger than the out-of-transit scatter.
    \label{fig:lc}
  }
\end{figure*}

The Kepler space telescope observed \sn\ at a 30-minute cadence from
2009 May 2 until 2013 April 8.  Data gaps during quarters 4, 9, and 13
led to an average duty cycle over the 3.9~year interval of 67\%.  \sn\
was also observed at 1-minute cadence from 2012 Oct 5 until 2013 Jan
11.  The top panel of Figure~\ref{fig:lc} shows a portion of the
30-minute cadence \texttt{PDCSAP} light curve.  Nonastrophysical
variability has been removed using the methods discussed by
\citet{smith_kepler_PDC_2017}; the default optimal aperture was
assumed \citep{smith_finding_2016}.  Cadences with non-zero quality
flags (9\% of the data) have been omitted.  The resulting photometry
is dominated by a quasi-periodic starspot signal with a peak-to-peak
amplitude that varies between 2\% and 8\%.  \added{Given that the secondary
companion's brightness in the Kepler band is $\approx$1.5\% that of the primary,
source confusion for the rotation signal is not expected to be
an issue.}
Previous analyses have
identified and characterized the smaller transit signal
\citep{2012ApJS..199...24T,thompson_planetary_2018}, validated its
planetary nature \citep{morton_false_2016}, and even searched the
system for transit timing variations \citep{holczer_transit_2016}.
Nonetheless, since the cluster membership provides us with more
precise stellar parameters than those previously available, we opted
to reanalyze the light curve.

@@

The most crucial parameters of a given star for our purposes are the
Gaia DR2 $\texttt{source\_id}$, the cluster or group name
($\texttt{cluster}$), and the $\texttt{age}$.  Given the hierarchical
nature of many stellar associations, we do not attempt to resolve the
cluster names to a single unique string.  The Orion complex for
instance can be divided into almost one hundred kinematic subgroups
\citep{kounkel_apogee2_2018}.  \added{Based on Figure~\ref{fig:XYZvtang}, the
\cn\ may also be part of a similar hierarchical association.} Similar complexity applies to the
problem of determining homogeneous ages, which we do not attempt to
resolve.  Instead, we simply merged the cluster names and ages
reported by various authors into a comma-separated string.
